Dominance Regions for Rank Two Cluster Algebras

### 2022-04-08 dominance_regions.tex
Typos

  \begin{lemma}
    \label{le:dominance inequalities}
    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is the polytope determined by the following inequalities:
    \begin{align}
      \label{ineq:1} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      \label{ineq:2} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:3} -u_{k-1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;
    \end{align}
    when $k>0$ and by the following inequalities:
    \begin{align*}
      u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1.
    \end{align*}
    when $k<0$.

@@

  We are now ready to prove Theorem~\ref{th:dominance inequalities}.
  The dominance region $\cP(\lambda)=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.

  To begin we rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
  For $k>0$, we get
  \begin{align*}
    u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
    u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
    -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
    -u_{k-1}^-(\mu_0-\lambda_0)-u_{k-2}^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1;
  \end{align*}
  and, for $k<0$, we get
  \begin{align*}
    u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
    u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
    u_k^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le bu_k^-\lambda_1;\\
    -u_{k+2}^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le cu_{k+1}^+\lambda_0+bu_k^-\lambda_1.
  \end{align*}
  The first inequality in each list is redundant so we drop them.
  Moreover, for $k=1$ the third and fourth inequalities in the first list are the same so we can increment $k$ in the last equality without losing any information and similarly for $k=-1$ in the second list. 
  This gives
  \begin{align*}
    u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
    -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
    -u_k^-(\mu_0-\lambda_0)-u_{k-1}^+(\mu_1-\lambda_1) &\le cu_{k+1}^+\lambda_0+bu_k^-\lambda_1;
  \end{align*}
  for $k>0$ and
  \begin{align*}
    u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
    u_k^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le bu_k^-\lambda_1;\\
    -u_{k+1}^-(\mu_0-\lambda_0)-u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1;
  \end{align*}
  for $k<0$.
  Then using that $-u_k^\varepsilon<0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$ we divide by these to rewrite the inequalities again as
  \begin{align}
    \label{ieq1} 0 & \le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
    \label{ieq2} -c\lambda_0 & \le \frac{u_{k-1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
    \label{ieq3} -(\mu_0-\lambda_0)-\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1) &\le c\frac{u_{k+1}^+}{u_k^-}\lambda_0+b\lambda_1;
  \end{align}
  and
  \begin{align}
    \label{ieq4} 0 &\le (\mu_0-\lambda_0)+\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1);\\
    \label{ieq5} b\lambda_1 &\le (\mu_0-\lambda_0)-\frac{u_{k+1}^+}{u_k^-}(\mu_1-\lambda_1);\\
    \label{ieq6} c\lambda_0+b\frac{u_{k-1}^-}{u_k^+}\lambda_1 &\le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).
  \end{align}
  We now study each sequence of inequalities in turn.

@@

  Similarly, the inequalities \eqref{ieq2} become more restrictive for $\mu_0\le0$ and $\mu_1\ge0$ as $k$ gets larger since the sequence of slopes $\frac{u_{k-1}^-}{u_k^+}$ is monotonically increasing and the intersection with \eqref{ieq1} moves lower on the $\mu_1$-axis as $k$ increases.
  Thus in the limit as $k\to\infty$, we obtain the inequality
  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
  determining a boundary of $\cP(\lambda)$.
  Observe further that $\mu_0-\lambda0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]

>>>>

  \begin{lemma}
    \label{le:dominance inequalities}
    For $k\in\ZZ$, $k\ne0$, and $\lambda\in\cI$, the region $\phi_k^{-1}\cC_k(\phi_k\lambda)\subset\RR^2$ is determined by the following inequalities:
    \begin{align}
      \label{ineq:1} u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      \label{ineq:2} u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:3} -u_{k-1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      \label{ineq:4} -u_{k-1}^-\mu_0-u_{k-2}^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;
    \end{align}
    when $k>0$ and by the following inequalities:
    \begin{align*}
      u_{k+1}^-\mu_0+u_k^+\mu_1 &\le u_{k+1}^-\lambda_0+u_k^+\lambda_1;\\
      u_k^-\mu_0+u_{k-1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      u_k^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;\\
      -u_{k+2}^-\mu_0-u_{k+1}^+\mu_1 &\le u_k^-\lambda_0+u_{k-1}^+\lambda_1;
    \end{align*}
    when $k<0$.

@@

  We are now ready to prove Theorem~\ref{th:dominance inequalities}.
  The dominance region $\cP(\lambda)=\bigcap_{k\in\ZZ}\phi_k^{-1}\cC_k(\phi_k\lambda)$ for $\lambda\in\cI$ is obtained by imposing all of the inequalities from Lemma~\ref{le:dominance inequalities} together with $\mu_0 -\lambda_0 \le 0$ and $0 \le \mu_1 - \lambda_1$ coming from $k=0$.

  To begin, observe that the boundary lines for \eqref{ineq:2} and \eqref{ineq:3} (and hence \eqref{ieq1} and \eqref{ieq2} below) intersect where $\mu_0=0$ and the boundary lines for \eqref{ineq:3} and \eqref{ineq:4} (and hence \eqref{ieq2} and \eqref{ieq3} below) intersect where $\mu_1=0$.
  We then rewrite the inequalities from Lemma~\ref{le:dominance inequalities} using the Chebyshev recursion.
  For $k>0$, we get
  \begin{align*}
    u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
    u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
    -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
    -u_{k-1}^-(\mu_0-\lambda_0)-u_{k-2}^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1;
  \end{align*}
  and, for $k<0$, we get
  \begin{align*}
    u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
    u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
    u_k^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le bu_k^-\lambda_1;\\
    -u_{k+2}^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le cu_{k+1}^+\lambda_0+bu_k^-\lambda_1.
  \end{align*}
  The first inequality in each list is redundant so we drop them.
  Moreover, for $k=1$ the third and fourth inequalities in the first list are the same so we can increment $k$ in the last equality without losing any information and similarly for $k=-1$ in the second list. 
  This gives
  \begin{align*}
    u_{k+1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le 0;\\
    -u_{k-1}^-(\mu_0-\lambda_0)+u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0;\\
    -u_k^-(\mu_0-\lambda_0)-u_{k-1}^+(\mu_1-\lambda_1) &\le cu_{k+1}^+\lambda_0+bu_k^-\lambda_1;
  \end{align*}
  for $k>0$ and
  \begin{align*}
    u_k^-(\mu_0-\lambda_0)+u_{k-1}^+(\mu_1-\lambda_1) &\le 0;\\
    u_k^-(\mu_0-\lambda_0)-u_{k+1}^+(\mu_1-\lambda_1) &\le bu_k^-\lambda_1;\\
    -u_{k+1}^-(\mu_0-\lambda_0)-u_k^+(\mu_1-\lambda_1) &\le cu_k^+\lambda_0+bu_{k-1}^-\lambda_1;
  \end{align*}
  for $k<0$.
  Then using that $-u_k^\varepsilon<0$ for $k>0$ and $u_k^\varepsilon<0$ for $k<0$ we divide by these to rewrite the inequalities again as
  \begin{align}
    \label{ieq1} 0 & \le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
    \label{ieq2} -c\lambda_0 & \le \frac{u_{k-1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1);\\
    \label{ieq3} -(\mu_0-\lambda_0)-\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1) &\le c\frac{u_{k+1}^+}{u_k^-}\lambda_0+b\lambda_1;
  \end{align}
  and
  \begin{align}
    \label{ieq4} 0 &\le (\mu_0-\lambda_0)+\frac{u_{k-1}^+}{u_k^-}(\mu_1-\lambda_1);\\
    \label{ieq5} b\lambda_1 &\le (\mu_0-\lambda_0)-\frac{u_{k+1}^+}{u_k^-}(\mu_1-\lambda_1);\\
    \label{ieq6} c\lambda_0+b\frac{u_{k-1}^-}{u_k^+}\lambda_1 &\le \frac{-u_{k+1}^-}{u_k^+}(\mu_0-\lambda_0)-(\mu_1-\lambda_1).
  \end{align}
  We now study each sequence of inequalities in turn.

@@

  Similarly, the inequalities \eqref{ieq2} become more restrictive for $\mu_0\le0$ and $\mu_1\ge0$ as $k$ gets larger since the sequence of slopes $\frac{u_{k-1}^-}{u_k^+}$ is monotonically increasing and the intersection with \eqref{ieq1} moves lower on the $\mu_1$-axis as $k$ increases.
  Thus in the limit as $k\to\infty$, we obtain the inequality
  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \]
  determining a boundary of $\cP(\lambda)$.
  Observe further that $\mu_0-\lambda_0 \le 0$ and $0 \le \mu_1-\lambda_1$ allow to strengthen this as
  \[ -c\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2b}(\mu_0-\lambda_0)-(\mu_1-\lambda_1) \le 0. \]
